Scalar Items in Embedded Position: {A}n Experimental Revisit

### 2012-07-07 text/paper/paper.tex
paper motivation section rewrite

On top of this, we would like to obtain further information about
the relative preferences among all putative readings, so as to be able
to decide between theoretical positions, as outlined in
Section~\ref{sec:theories-predictions}. Neither of the previous
studies gives us that, either because they simply have not
investigated all the relevant comparisons
(\citet{GeurtsPouscoulous2009:Embedded-Implic},
\citet{CliftonDube2010:Embedded-Implic}), or because they cannot safely
derive the required cardinal information for danger of conflating
preferences for readings with preferences for pictures
(\citet{ChemlaSpector2010:Experimental-Ev}, our pilot study).

Another desideratum for a further empirical testing is that a study
aimed at revealing information about availability and preferences of
readings be accompanied by a suitable comparable investigation into a
phenomenon which is know to allow for several readings with a given
known preferences structure. This way and only this way can a proper
baseline be established to guide the interpretation of the observed
data.

Moreover, a final omission of previous studies is that they did not
control for possible conflating effects of ``silent intonation''
(XYZ)\dn{references}. Even traditionalism maintains that local
readings are attested, but requiring a contrastive stress on the
scalar item
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar}. Variation
in the interpretation of target sentences therefore could be caused by
subjects imposing different intonational patterns on the visually
presented target sentences. Ideally, we should therefore present
sentences auditorily and address directly the frequently voiced
hypothesis that local readings are triggered by contrastive
stress.\dn{relate to \citet{SchwarzClifton2008:Strengthening-o} and
  others?}

@@

\begin{itemize}
\item The distribution of
responses found in previous studies could in part be explained by
differences in typicality of the pictures with respect to the possible
readings (see van Tiel). In the present case this kind of reasoning
would have to be extended to the typicalilty of parts of pictures. On
intuitive grounds, we take this kind of reasoning to be
implausible. We will now shortly discuss how graphical properties
might still affect judgments in the worst case. In the first step of
the \as-condition local and global readings cannot be judged,
yet. Therefore, graphical properties should not affect judgments if
participants have one of these readings in mind. If participants have
a literal reading in mind, the worst case scenario is that they
refrain from judging the sentence as true at this point due to some,
eg. atypical, graphical property of the picture. The situation is
similar at the second step. The local reading is still not
decidable. Therefore, graphical properties should not play a role if
participants have a local reading in mind. A positive judgment might,
however, be a delayed judgment of a literal reading. Again, the worst
case scenario for our purpose is that participants refrain from
answering because of graphical properties. At the last step the local
reading requires a negative judgment. Now, we could obtain delayed
negative responses from literal or global readings because the graph
as a whole is, e.g., logically true but atypical with respect to these
readings. These kinds of judgments would be indistinguishable from
local responses. Note, however, that we have no reason to believe that
typicality has large effects, because, given the results from van
Tiel, the picture as a whole is expected to be one of the more typical
situations for \as-sentences. Still, we cannot exclude the possibility
that graphical properties of the pictures might have the described
effect. In the \es-conditions this type of effect is, however,
entirely impossible since the literal and global reading is plainly
false given the initial parts as well as the whole graph. Summing up,
in the worst case, which we consider implausible, graphical effects
might lead to an enhanced number of local responses in the \as- as
compared to the \es-condition. We have to keep this possibility in
mind. We want to stress, however, that the design presented here
improves on previous studies with respect to possible graphical
effects.
\end{itemize}

>>>>

On top of this, we would like to obtain further information about the
relative preferences among all putative readings, so as to be able to
decide between theoretical positions, as outlined in
Section~\ref{sec:theories-predictions}. Neither of the previous
studies gives us that, either because they simply have not
investigated all the relevant comparisons
(\citet{GeurtsPouscoulous2009:Embedded-Implic},
\citet{CliftonDube2010:Embedded-Implic}), or because they run risk of
conflating preferences for readings with preferences for pictures
(\citet{ChemlaSpector2010:Experimental-Ev}, our pilot study).

% Another desideratum for a further empirical testing is that a study
% aimed at revealing information about availability and preferences of
% readings be accompanied by a suitable comparable investigation into a
% phenomenon which is know to allow for several readings with a given
% known preferences structure. This way and only this way can a proper
% baseline be established to guide the interpretation of the observed
% data.

Another potential shortcoming of previous studies is that they did not
control for possible conflating effects of ``silent intonation''
(XYZ)\dn{references}. Even traditionalism maintains that local
readings are attested, but requiring a contrastive stress on the
scalar item
\citep[e.g.][]{Horn2006:The-Border-Wars,Geurts2009:Scalar-Implicat,Geurts2010:Quantity-Implic,Tielvan-Tiel2012:Embedded-Scalar}. Variation
in the interpretation of target sentences therefore could be caused by
subjects imposing different intonational patterns on the visually
presented target sentences. Ideally, we should therefore present
sentences auditorily and address directly the frequently voiced
hypothesis that local readings are triggered by contrastive
stress.\dn{relate to \citet{SchwarzClifton2008:Strengthening-o} and
  others?}

@@

\begin{itemize}
\item The distribution of
responses found in previous studies could in part be explained by
differences in typicality of the pictures with respect to the possible
readings (see van Tiel). In the present case this kind of reasoning
would have to be extended to the typicalilty of parts of pictures. On
intuitive grounds, we take this kind of reasoning to be
implausible. We will now shortly discuss how graphical properties
might still affect judgments in the worst case. In the first step of
the \as-condition local and global readings cannot be judged,
yet. Therefore, graphical properties should not affect judgments if
participants have one of these readings in mind. If participants have
a literal reading in mind, the worst case scenario is that they
refrain from judging the sentence as true at this point due to some,
eg. atypical, graphical property of the picture. The situation is
similar at the second step. The local reading is still not
decidable. Therefore, graphical properties should not play a role if
participants have a local reading in mind. A positive judgment might,
however, be a delayed judgment of a literal reading. Again, the worst
case scenario for our purpose is that participants refrain from
answering because of graphical properties. At the last step the local
reading requires a negative judgment. Now, we could obtain delayed
negative responses from literal or global readings because the graph
as a whole is, e.g., logically true but atypical with respect to these
readings. These kinds of judgments would be indistinguishable from
local responses. Note, however, that we have no reason to believe that
typicality has large effects, because, given the results from van
Tiel, the picture as a whole is expected to be one of the more typical
situations for \as-sentences. Still, we cannot exclude the possibility
that graphical properties of the pictures might have the described
effect. In the \es-conditions this type of effect is, however,
entirely impossible since the literal and global reading is plainly
false given the initial parts as well as the whole graph. Summing up,
in the worst case, which we consider implausible, graphical effects
might lead to an enhanced number of local responses in the \as- as
compared to the \es-condition. We have to keep this possibility in
mind. We want to stress, however, that the design presented here
improves on previous studies with respect to possible graphical
effects.
\item Strictly speaking, directly comparing the results of all
  relevant empirical studies is not feasible for a number of
  reasons. Firstly, all of the previous studies were conducted in
  different languages. \citet{GeurtsPouscoulous2009:Embedded-Implic}
  tested Dutch material, \citet{CliftonDube2010:Embedded-Implic}
  English, \citet{ChemlaSpector2010:Experimental-Ev} French, and we
  tested German material. Although quantity implicatures are usually
  considered a universal phenomenon, derived from general principles
  of efficient language use and/or organization, it might nonetheless
  be that different languages show slightly different patterns of
  data, because there might be relevant differences in the set of
  available quantifiers.\dn{spell out?} Secondly, we must be careful
  to compare studies directly, because of methodological concerns. For
  instance, not only the pictorial material might influence judgement
  patterns, also the filler material might. If the fillers used are
  all very clear to elicit a \emph{true}- or \emph{false}-judgement,
  then subtle meaning differences in the target conditions might more
  easily be smothered. On the other hand, if the filler material is
  also subtly ambiguous, potential meaning differences in the target
  material could be accented. In other words, it might be that the
  filler material, as it were, could influence the \mymark{standard of
    precision} for applicability of the predicates \emph{true} and
  \emph{false}. (Indeed, we believe that, when it comes to subjects'
  responses in psycholinguistic experiments, \emph{truth-of-a-sentence} is a
  vague notion.\dn{reference!})
\end{itemize}
